---
title: "HW02_Assignment1: Exercise 2 and 3"
output:
  pdf_document: default
  html_document:
    keep_md: yes
editor_options:
  chunk_output_type: inline
---

```{r allow errors, echo = FALSE}
knitr::opts_chunk$set(error = TRUE)
```

```{r load packages, warning = FALSE, message = FALSE}
library(ggplot2)
library(tidyverse)
library(datasets)
library(tibble)
library(gapminder)
```

#Exercises 2 and 3

# Pick one quantitative variable out of dataset Gapminder - Population
## What is the range in Population? 

```{r}
  summarise(gapminder, minpop = min(pop), maxpop=max(pop))
```

## What is the mean population? 

```{r}
  summarise(gapminder, meanpop = mean(pop))
```


## Graph of data spread - Population in Canada from 1952 - 2007

```{r}
gapminder %>% 
  filter(country == 'Canada') %>% 
  arrange(year) %>% 
  ggplot(aes(year,pop))+
  geom_line()+
  ylab("Population of Canada")+
  xlab("Year")
```


# Pick one categorical variable out of dataset HairEyeColour - Eye Colour 
## What are the ranges in eye colour? 
```{r}
HairEyeColor %>% 
  as_tibble() %>% 
  distinct(Hair) 
```


```{r}
HEC = HairEyeColor %>% 
  as_tibble()
```

## Plot the distribution of Hair Colour in a bar graph to fulfill Exercise 3 requirement

```{r}
HEC %>% 
  ggplot(aes(Hair, weight = n, fill = Sex))+
  geom_bar(position = "dodge") +
  ylab("Frequency of Hair Colour") +
  xlab("Hair Colour")
```

## Plot the distribution of life expectancy in American (North and South) countries from 2000 - 2007 vs GDP

```{r}
gapminder %>% 
  filter(continent == 'Americas', year >= 2000) %>% 
  arrange(year) %>% 
  ggplot(aes(gdpPercap, lifeExp, colour = country)) +
    geom_point() +
    geom_smooth(method = lm, se = FALSE) +
    scale_x_log10() +
    xlab('GDP') +
    ylab('Life Expectancy')

```

